Group 5 Report

### 2022-08-02 Report/Group 5 report.Rmd
Proofreading and editing.

This report describes the group's approach to the problem statement and
our findings. First, the problem statement is presented, then the
brainstorming and data collection processes are elaborated, before data
description and findings are presented. Lastly, limitations and steps
forward, as well as a summary of our experience.

@@

The project chosen for our group was Oslo Philanthropic Exchange (OPX), 
a startup working to develop solutions to assist individuals and 
organizations wanting to donate to charities and designing a socially 
responsible investment strategy.  Their main goal is to increase cash 
flow from private to charitable purposes. Therefore, the donor's trust 
in the charities’ abilities to carry out their promises is significant.

To do this, data from charities need to be collected. OPX’s current 
challenge is the data collection, which must be collected manually today
since the data is unstructured. Therefore, they wanted a way to automate 
the data collection, using web scraping.

Additionally, by creating KPIs (Key Performance Indicator), OPX can use 
them to benchmark the relationship between financial assets and emergency 
relief obligations.

@@

1. Automating the data collection will streamline the work of OPX 
and create more transparency which enhances trust in charities.

2. Creating KPI(s) is important for the organization’s performance 
management, to influence the objective, and to foster growth.

@@

Our brainstorming process for this case was characterized by several
surprises and turns in the direction of the solution. As we dug deeper
into the solution opportunities, we were also met by new obstacles that
forced us to change course. In particular, there were four turning
points. Therefore, we have decided to divide the brainstorming into
three phases.

## Phase 1: How to harvest and analyze the data? {.smaller}

OPX wanted us to harvest the organizations' financial data from the web.
During the first stage of brainstorming, we wanted to find a simple and
automated way to do so.

We discussed creating a webcrawler that could collect data across
different websites, but quickly decided that this would be too
difficult, and that it would only work with selected organizations. The
suggested solution was to create a code that could read PDF documents
that OPX downloaded themselves. Our code would analyze and organize the
uploaded data from the PDF documents.

However, different organizations publish financial data in different
ways in their yearly reports -- some financial statements were included
as tables, some as pictures, etc. This led us to phase 2.

@@

At this stage, we wanted to explore alternatives to analyzing PDF
documents. We discussed how to do so, and concluded that we had three
options:

@@

We divided the task among ourselves to explore whether these solutions
were feasible or not. The first option of using PDF documents still had
the issue of financial statements not always being published as text.
Also, we quickly found that Proff.no disallowed webscraping on their
website. The Brønnøysund registry does offer API access to all the financial statements, but we discovered that access to costs NOK 480,000.

We started to look at workarounds for this problem. It would still be
possible to download Proff.no HTML websites manually for each
organization. We did receive some XML files from Statistics Norway, but using these is ultimately not a viable solution for OPX.

The Brønnøysund registry and Proff.no had different divisions of
accounting items than the ones OPX wanted. We found that we needed to
create an item path from the webpage items to the OPX items, and we
attempted to do so in Excel at first, so that we later could code this
into R. While doing so, we realized that it would be practically
impossible to extract the correct sums for the OPX accounting items from
the Brønnøysund items. This was e.g. because OPX had split the operating
income into public and private contributions, while the Brønnøysund
registry and Proff.no had not.

@@

When also discovering that not all organizations publish their financial
statements, and certainly not for every year, we decided to give up on
collecting financial data for OPX. This is when we moved on to the third
and final stage.

@@

In order to create a somewhat more challenging task for ourselves, we
also decided to create a shiny app that OPX could use, which would
display the KPIs as well as financial trends for the selected
organization. To use this, OPX needs to gather the financial data
themselves, then upload this into the shiny app as a x document

@@

We wanted to use webscraping to collect the data, so that we could have
automated the data input process. As described, we explored different
potential solutions. We experimented on coding such that data could have
been imported from XML files. However, once we realized that the
financial data was of little ¨use, this experimentation stopped.

>>>>

This report describes the group's approach to the problem statement and
our findings. First, the problem statement is presented, then the
brainstorming and data collection processes are elaborated, before data
description and findings are presented. Lastly, we discuss limitations and steps
forward, and provide a brief summary of our experience.

@@

The project chosen for our group was Oslo Philanthropic Exchange (OPX), 
a startup working to develop solutions to assist individuals and 
organisations wanting to donate to charities and designing a socially 
responsible investment strategy. Their main goal is to increase cash 
flow from private groups and individuals to charitable purposes. Therefore, the donor's trust 
in the charities’ abilities to carry out their promises is of paramount significance.

To do this, data from charities need to be collected. OPX’s current 
challenge is data acquisition, as data currently must be collected manually. They therefore wanted a way to automate data collection, for example using web scraping.

 <!-- Needs work -->
Additionally, by creating Key Performance Indicators based on these data, OPX can use 
them to benchmark the relationship between financial assets and emergency 
relief obligations.

@@

1. Automating the data collection will streamline the work of OPX 
and create more transparency, which enhances trust in charities.

2. Creating KPI(s) is important for the organization’s performance 
management, to influence its objectives, and to foster growth.

@@

Our brainstorming process for this case was characterised by several
surprises and turns in the direction of the solution. As we dug deeper
into the solution opportunities we were also met by new obstacles that
forced us to change course. In particular, there were four turning
points. Therefore, we have decided to divide the brainstorming section into
three phases.

## Phase 1: How to harvest and analyse the data? {.smaller}

OPX wanted us to harvest the organisations' financial data from the web.
During the first stage of brainstorming, we wanted to find a simple and
automated way to do so.

We discussed creating a webcrawler that could collect data across
different websites, but quickly decided that this would be too
difficult, and that it would only work with selected organizations. The next
suggested solution was to create code that could read PDF documents
that OPX downloaded themselves. Our code would analyse and organise the
uploaded data from the PDF documents.

However, different organisations publish financial data in different
ways in their annual reports -- some financial statements were included
as tables, some as pictures, etc. This led us to phase 2.

@@

At this stage, we wanted to explore alternatives to analysing PDF
documents. We discussed how to do so, and concluded that we had three
options:

@@

We divided the task among ourselves to explore whether these solutions
were feasible or not. The first option of using PDF documents still had
the issue of financial statements not always being published as text, as well as their often wildly differing formats.
Unfortunately, we quickly found that Proff.no disallows any automated collection of data from their website. The Brønnøysund registry does offer API access to all the financial statements, but we discovered that access currently costs NOK 480,000.

We started to look at workarounds for this problem. It could still be
possible to download Proff.no HTML websites manually for each
organisation. We did receive some XML files from Statistics Norway, but using these is ultimately not a viable solution for OPX.

The Brønnøysund registry and Proff.no had different divisions of
accounting items than the ones OPX wanted. We found that we needed to
create an item path from the webpage items to the OPX items, and we
attempted to do so in Excel at first, so that we later could code this
into R. While doing so, we realised that it would be practically
impossible to extract the correct sums for the OPX accounting items from
the Brønnøysund items. This was e.g. because OPX had split the operating
income into public and private contributions, while the Brønnøysund
registry and Proff.no had not.

@@

When also discovering that not all organisations publish their financial
statements, and certainly not for every year, we decided to give up on
collecting financial data for OPX, as the task turned out to impossible given current reporting requirements and practices. This is when we moved on to the third
and final stage.

@@

In order to create a somewhat more challenging task for ourselves, we
also decided to create an interactive dashboard based on Shiny that OPX could use, which would
display the KPIs as well as financial trends for the selected
organisation. To use this, OPX needs to gather the financial data
themselves, as well as download data manually from Proff.no, and then upload this into the dashboard in the form of Excel and HTML documents.

@@

We wanted to use webscraping to collect the data, so that we could have
automated the data input process. As described, we explored different
potential solutions. We experimented on coding such that data could have
been imported from XML files. However, once we realised that the
financial data was of little use, this experimentation stopped.
